Leveraging Diversity to Find Bugs in JavaScript Engines

### 2019-06-20 paper/abstract.tex
pass on abstract and intro
pass on paper

%reports on a study we ran to 
This paper evaluates the importance of
diversity to find functional bugs in JavaScript engines. For that, we
explored two simple diversity-aware techniques---test transplantation and
cross-engine differential testing. The first technique runs test
suites of a given engine in another engine. The second technique
fuzzes existing inputs and then compares the output produced by
different engines with a differential oracle.

\sloppy
We considered engines from four major players in our
experiments--Apple, Google, Microsoft, and Mozilla. Our results
indicate that both techniques revealed several bugs, many of which
confirmed by developers. We reported \noBugsTransplantation{} bugs
with test transplantation (\noBugsTransplantationConfirmed{} of these bugs
confirmed and \noBugsTransplantationFixed{} fixed) and reported
\noBugsDifferentialTesting{} bugs with differential testing
(\noBugsDifferentialTestingConfirmed{} of these confirmed
and \noBugsDifferentialTestingFixed{} fixed). Results indicate that
most of these bugs affected two engines--Apple's
\jsc{} and Microsoft's \chakra{}. To sum, our results show that
diversity-aware techniques are easy to apply and very effective in
finding bugs in complex software, such as JavaScript engines.

%% Although more research needs to be done to optimizie 
%% warning triaging,

%% ; we found
%% only \Fix{one} bug in Google \veight{} and none in Mozilla's
%% \smonkey{}

>>>>

\sloppy
This paper evaluates the importance of
diversity to find functional bugs in JavaScript engines. For that, we
explored two existing diversity-aware techniques---test transplantation and
cross-engine differential testing. The first technique runs test
suites of a given engine in another engine. The second technique
fuzzes existing inputs and then compares the output produced by
different engines with a differential oracle.
We considered engines from four major players in our
experiments--Apple, Google, Microsoft, and Mozilla. Our results
indicate that both techniques revealed several bugs, many of which
confirmed by developers. We reported \noBugsTransplantation{} bugs
with test transplantation (\noBugsTransplantationConfirmed{} of these bugs
confirmed and \noBugsTransplantationFixed{} fixed) and reported
\noBugsDifferentialTesting{} bugs with differential testing
(\noBugsDifferentialTestingConfirmed{} of these confirmed
and \noBugsDifferentialTestingFixed{} fixed). Results indicate that
most of these bugs affected two engines--Apple's
\jsc{} and Microsoft's \chakra{}. To sum, our results show that
diversity-aware techniques are easy to apply and very effective in
finding bugs in complex software, such as JavaScript engines.

### 2019-06-20 paper/paper.tex
pass on paper

@@

\usepackage{booktabs}
\usepackage{multirow}
\usepackage{tikz}
\usetikzlibrary{matrix,fit,shapes,calc,positioning,shadows,arrows,shapes,backgrounds,decorations.markings,fadings}
\usepackage{listings}
\usepackage[caption=false, font=footnotesize]{subfig}
%%%%%%%%%%%%% code listing
\renewcommand{\ttdefault}{pcr}
\lstset{
  basicstyle=\scriptsize\ttfamily,
  keywordstyle=\scriptsize\ttfamily\bfseries,
  language=Java,             % choose the language of the code
  frame=single,              % adds a frame around the code
  aboveskip=0pt,
  belowskip=0pt,
  breaklines=true,           % sets automatic line breaking
  breakatwhitespace=false,   % sets if automatic breaks should only happen at
  showspaces=false,
  %numbersep=5pt,              % Abstand der Nummern zum Text
  %tabsize=2,                  % Groesse von Tabs
  %extendedchars=true,         %
  %breaklines=true,            % Zeilen werden Umgebrochen
  keywords=[2]{class, incorporateUserFeedback, testPushPop, testPopPush},
}
\usepackage{balance}
\usepackage{wrapfig}
\usepackage{enumitem}
\usepackage{url}

@@

%% It automates test generation in scenarios where multiple
%% implementations of a system exist. DT leverages diversity across
%% system's implementations to detect anomalous behavior.
\emph{Related Ideas.}~The idea of test set diversity dates back to the
eighties~\cite{white-cohen-tse1980, ostrand-balcer-1988}. In contrast
to prior work on this topic, this paper explores diversity of
implementations and diversity of sources of test cases as opposed to
diversity of the test cases themselves. Section~\ref{sec:related:diversity-testing}
elaborates related work on this topic. Differential
Testing~\cite{Brumley-etal-ss07} (DT) has been applied in a variety of
contexts to find
bugs~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17,Zhang:2017:ATD:3097368.3097448}.
It has shown to be specially practical in scenarios where the
observation of difference gives a strong signal of a real problem. For
example, Mozilla runs JS files against different configurations of a
given build of their \smonkey\ engine (\eg{}, trying to enable or not
eager JIT compilation\footnote{These files are created with the
  grammar-based fuzzer jsfunfuzz~\cite{jsfunfuzz}. Look for option
  ``compare\_jit'' from funfuzz.}). A positive aspect of the approach
is that it can be fully automated---as only one engine is used, the
outcomes of the test in both configurations are expected to be
identical. The Mozilla team uses this approach since 2002; they have
been able to find over 270 bugs since
then~\cite{jsfunfuzz-at-mozilla}, including security
bugs. Cross-engine differential testing, in contrast, has not been
widely popularized. One possible reason is that it is still not
practical to fully automate the technique. In contrast to other
applications of differential testing, a number of legitimate reasons
exist, other than a bug, for a test execution to manifest discrepancy
(see Tables~\ref{fig:piecharts-transplantation} and
~\ref{tab:false-positives}). To sum, variations of these ideas have
been explored before in different contexts.  The goal of the paper is
to assess the ability of the techniques aforementioned in finding bugs
on \javascript\ engines.

@@

\vspace{1ex} To sum, this paper provides initial, yet strong evidence
that exploring diversity should be encouraged to find functional bugs
in JavaScript engines.

@@

Generational fuzzers are typically grammar-based. These fuzzers
generate a new file using the grammar of the language whose inputs
should be fuzzed. Intuitively, those fuzzers implement a traversal of
the production rules of the input grammar to create syntax trees,
which are then pretty-printed. Consequently, this approach produces
inputs that are syntactically valid by construction. We analyzed four
grammar-based fuzzers--Grammarinator~\cite{grammarinator},
jsfunfuzz~\cite{jsfunfuzz},
LangFuzz~\cite{Holler:2012:FCF:2362793.2362831}, and
Megadeth~\cite{grieco2016quickfuzz}.  Unfortunately, none of those
were effective out of the box. For example, we produced 100K inputs
with Grammarinator and only few inputs were valid. With Megadeth, we
were able to produce more\Comment{ \Fix{Y, Y$>$Y?}} valid inputs as it
contains some heuristics to circumvent violations of certain typing
rules.\Comment{ such as \Fix{variable used must be defined?}.}
Nonetheless, running those inputs in our infrastructure we were unable
to find discrepancies. Inspecting those inputs, we realized that they
reflected very simple scenarios. To sum, a high percentage of inputs
that Grammarinator and Megadeth generated were semantically-invalid
that we needed to discard whereas the valid inputs manifested no
discrepancies. Considering jsfunfuzz~\cite{jsfunfuzz}, we noticed
that, in addition to the issues mentioned above, it produces inputs
that use functions that are only available in the \smonkey{}
engine. We would need either to mock those functions in other engines
or to discard those tests. Considering
LangFuzz~\cite{Holler:2012:FCF:2362793.2362831}, the tool is not
publicly available. Another fundamental issue associated with
generational fuzzers in our context is that the tests they produce do
not contain assertions; to enable the integration of this kind of
fuzzers in our infrastructure---we would need to look for
discrepancies across compiler error messages as opposed to assertion
violations.  All in all, although grammar-based fuzzers have been
shown effective to find real
bugs~\cite{Holler:2012:FCF:2362793.2362831}, we did not consider those
fuzzers in this study for the reasons above.

@@

We used two black-box mutational fuzzers in this
study--\radamsa~\cite{radamsa} and \quickfuzz~\cite{quickfuzz}. These
fuzzers require no instrumentation and domain-knowledge. They mutate
existing inputs randomly. The strength of the approach is
limited by the quality of the test suite and the supported mutation
operators, which are typically simple. We chose these specific fuzzers
because, conceptually, one complements the other. \quickfuzz\ creates
mutations like \radamsa. However, in contrast to \radamsa, \quickfuzz\ is aware
of the \js\ syntax; it is able to replace subtrees of the syntax
tree~\cite{grieco2016quickfuzz} with trees created anew.

@@

\vspace{1ex}
\noindent\textbf{Acknowledgments.~}Igor was supported by the FACEPE
fellowship \Fix{...}  This research was partially funded by INES 2.0,
FACEPE grants PRONEX APQ 0388-1.03/14 and APQ-0399-1.03/17, and CNPq
grant 465614/2014-0.

\balance
\bibliographystyle{elsarticle-num}
\bibliography{references,../docs/google-research-awards-latam/tmp}

@@

>>>>

%% avoid footnotes across pages
\interfootnotelinepenalty=10000
%\raggedbottom

@@

%% paragraphs within margins
\usepackage[english]{babel}
\setlength{\emergencystretch}{2pt}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{tikz}
\usetikzlibrary{matrix,fit,shapes,calc,positioning,shadows,arrows,shapes,backgrounds,decorations.markings,fadings}
\usepackage{listings}
\usepackage[caption=false, font=footnotesize]{subfig}
%%%%%%%%%%%%% code listing
\renewcommand{\ttdefault}{pcr}
\lstset{
  basicstyle=\scriptsize\ttfamily,
  keywordstyle=\scriptsize\ttfamily\bfseries,
  language=Java,             % choose the language of the code
  frame=single,              % adds a frame around the code
  aboveskip=0pt,
  belowskip=0pt,
  breaklines=true,           % sets automatic line breaking
  breakatwhitespace=false,   % sets if automatic breaks should only happen at
  showspaces=false,
  %numbersep=5pt,              % Abstand der Nummern zum Text
  %tabsize=2,                  % Groesse von Tabs
  %extendedchars=true,         %
  %breaklines=true,            % Zeilen werden Umgebrochen
  keywords=[2]{class, incorporateUserFeedback, testPushPop, testPopPush},
}
\usepackage{balance}
\usepackage{wrapfig}
\usepackage{enumitem}
\usepackage{url}

@@

%% It automates test generation in scenarios where multiple
%% implementations of a system exist. DT leverages diversity across
%% system's implementations to detect anomalous behavior.
\emph{Related Ideas.}~The idea of test set diversity dates back to the
eighties~\cite{white-cohen-tse1980, ostrand-balcer-1988}. In contrast
to prior work on this topic, this paper explores diversity of
implementations and diversity of sources of test cases as opposed to
diversity of the test cases themselves. Section~\ref{sec:related:diversity-testing}
elaborates related work on this topic. Differential
Testing~\cite{Brumley-etal-ss07} (DT) has been applied in a variety of
contexts to find
bugs~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17,Zhang:2017:ATD:3097368.3097448}.
It has shown to be specially practical in scenarios where the
observation of difference gives a strong signal of a real problem. For
example, Mozilla runs JS files against different configurations of a
given build of their \smonkey\ engine (\eg{}, trying to enable or not
eager JIT compilation\footnote{These files are created with the
  grammar-based fuzzer jsfunfuzz~\cite{jsfunfuzz}. Look for option
  ``compare\_jit'' from funfuzz.}). A positive aspect of the approach
is that it can be fully automated---as only one engine is used, the
outcomes of the test in both configurations are expected to be
identical. The Mozilla team uses this approach since 2002; they have
been able to find over 270 bugs since
then~\cite{jsfunfuzz-at-mozilla}, including security
bugs. Cross-engine differential testing, in contrast, has not been
widely popularized. One possible reason is that it is still not
practical to fully automate the technique. In contrast to other
applications of differential testing, a number of legitimate reasons
exist, other than a bug, for a test execution to manifest discrepancy
(see Tables~\ref{fig:piecharts-transplantation} and
~\ref{tab:false-positives}). To sum up, variations of these ideas have
been explored before in different contexts.  The goal of the paper is
to assess the ability of the techniques aforementioned in finding bugs
on \javascript\ engines.

@@

\vspace{1ex} To summarize, this paper provides initial, yet strong evidence
that exploring diversity should be encouraged to find functional bugs
in JavaScript engines.

@@

Generational fuzzers are typically grammar-based. These fuzzers
generate a new file using the grammar of the language whose inputs
should be fuzzed. Intuitively, those fuzzers implement a traversal of
the production rules of the input grammar to create syntax trees,
which are then pretty-printed. Consequently, this approach produces
inputs that are syntactically valid by construction. We analyzed four
grammar-based fuzzers--Grammarinator~\cite{grammarinator},
jsfunfuzz~\cite{jsfunfuzz},
LangFuzz~\cite{Holler:2012:FCF:2362793.2362831}, and
Megadeth~\cite{grieco2016quickfuzz}.  Unfortunately, none of those
were effective out of the box. For example, we produced 100K inputs
with Grammarinator and only few inputs were valid. With Megadeth, we
were able to produce more\Comment{ \Fix{Y, Y$>$Y?}} valid inputs as it
contains some heuristics to circumvent violations of certain typing
rules.\Comment{ such as \Fix{variable used must be defined?}.}
Nonetheless, running those inputs in our infrastructure we were unable
to find discrepancies. Inspecting those inputs, we realized that they
reflected very simple scenarios. To sum up, a high percentage of inputs
that Grammarinator and Megadeth generated were semantically-invalid
that we needed to discard whereas the valid inputs manifested no
discrepancies. Considering jsfunfuzz~\cite{jsfunfuzz}, we noticed
that, in addition to the issues mentioned above, it produces inputs
that use functions that are only available in the \smonkey{}
engine. We would need either to mock those functions in other engines
or to discard those tests. Considering
LangFuzz~\cite{Holler:2012:FCF:2362793.2362831}, the tool is not
publicly available. Another fundamental issue associated with
generational fuzzers in our context is that the tests they produce do
not contain assertions; to enable the integration of this kind of
fuzzers in our infrastructure---we would need to look for
discrepancies across compiler error messages as opposed to assertion
violations.  All in all, although grammar-based fuzzers have been
shown effective to find real
bugs~\cite{Holler:2012:FCF:2362793.2362831}, we did not consider those
fuzzers in this study for the reasons above.

@@

We used two black-box mutational fuzzers in this
study--\radamsa~\cite{radamsa} and \quickfuzz~\cite{quickfuzz}. These
fuzzers require no instrumentation and domain-knowledge. They mutate
existing inputs randomly. The strength of the approach is
limited by the quality of the test suite and the supported mutation
operators, which are typically simple. We chose these specific fuzzers
because, conceptually, one complements the other. \quickfuzz\ creates
mutations like \radamsa. However, in contrast to \radamsa, \quickfuzz\ is aware
of the \js\ syntax; it is able to replace sub-trees of the syntax
tree~\cite{grieco2016quickfuzz} with trees created anew.

@@

\vspace{1ex}
\sloppy
\noindent\textbf{Acknowledgments.~}Igor is supported by the FACEPE
fellowship IBPG-0123-1.03/17. This research was partially funded by
INES 2.0, FACEPE grants PRONEX APQ 0388-1.03/14 and APQ-0399-1.03/17,
and CNPq grant 465614/2014-0.

\balance
\bibliographystyle{elsarticle-num}
\bibliography{references,tmp}

@@

%%  LocalWords:  IoT DT JS JIT fuzzer jsfunfuzz jit funfuzz bytecodes
%%  LocalWords:  JavaScriptCore JScript Ecma toPrecision Kangax JSVU
%%  LocalWords:  cccrr WebKit ReferenceError TypeError lineNumber sep
%%  LocalWords:  drainMicrotasks ccrrrr Duktape js runtime formedness
%%  LocalWords:  NN NLP vec embeddings perceptron arrowed toolchain
%%  LocalWords:  fuzzers eshost cli pre ArrayBuffer RangeError getInt
%%  LocalWords:  ToIndex Clusterization byteOffset SpiderMonkey AFL
%%  LocalWords:  DataView setInt Radamsa QuickFuzz Grammarinator
%%  LocalWords:  LangFuzz Megadeth libFuzzer sanitizers
